Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-08 manuscript.tex
update to wedge figure/caption

\begin{figure}[t]
\centerline{
\includegraphics[height=3in]{plots/wedgeWithBG.png}
}
\caption{Foregrounds are a primary challenge facing 21\,cm cosmology experiments. 
HERA leverages a ``wedge'' in the spherically-averaged ($\mathbf{k}$ is broken into $k_\|$ and $k_\perp$) power spectrum (center panel; \citealt{dillon_et_al2015}). Smooth-spectrum foregrounds (right panel) $\sim$5 orders of magnitude brighter than fiducial EoR models (left panel; \citealt{mesinger_et_al2011}) create the ``wedge'' when they interact with the interferometer's chromatic response. By avoiding foregrounds, PAPER has placed limits within an order
of magnitude (in mK) of these models \citep{ali_et_al2015} and show the ``EoR Window'' to be foreground-free.
HERA's dish and configuration optimize wedge/window isolation and direct sensitivity to low-$k_\perp$ modes where EoR is brightest.
%v2
Cartoon of the wedge.  The gray rectangle represents the smooth-spectrum foregrounds as they would be if the instrument had a perfect achromatic response.  The pink wedge area shows the chromatic response of the interferometer, where additional power is thrown up from the gray region to higher k-values with increasing baseline.  The additional horizontal pink line illustrates the affect that other systematics, such as reflections on cables, can have in contaminating the measurement.  The white region shown the 'eor window', where the measurement is not contaminated by foregrounds or systematics.}
\label{fig:wedge}
\end{figure}

>>>>

\begin{figure}[t]
\centerline{
\includegraphics[height=3in]{plots/wedges.pdf}
}
\caption{The EoR ``window'' and foreground ``wedge'' are shown in this plot, which splits the wavenumber into $\kvpr$ (horizontal) and $\kpar$ (vertical) components.
Smooth-spectrum foregrounds with an intrinsic spectrum indicated by the gray bar along the bottom create the ``wedge'' when they interact with the interferometer's chromatic response, shown with a foreground image from the MWA.  Systematics can extend the wedge to the upper left.  The EoR window (shown with a simulation
from \cite{mesinger_et_al2011}) to the upper left should be free from foregrounds.}
\label{fig:wedge}
\end{figure}
